Investigating Overfitting in Convolutional Neural Networks

### 2025-05-22 paper_formatted.tex
added a formatted version of the paper for better aesthetics, the formatting still needs to be slightly fixed on the nonformatted one (the one to submit)

% !Author = JustinMa
% !Date = 5/19/25

@@

@@

    \centerline{\textbf{Investigating Overfitting in Convolutional Neural Networks}}

    \noindent\textbf{1. Introduction}

@@

    \noindent\textbf{2. Statistical Question}

@@

    \noindent\textbf{3. Data Collection}

@@

    \noindent\textbf{Data Display}

    \noindent\textbf{Data Analysis}

    \noindent\textbf{Conclusion}

    \noindent\textbf{Reflection}

>>>>

%! Author = JustinMa
%! Date = 5/22/25

@@

\title{Investigating Overfitting in Convolutional Neural Networks}\date{}

@@

    \maketitle

    \section*{1. Introduction}

@@

    \section*{2. Statistical Question}

@@

    \section*{3. Data Collection}

@@

    \section*{4. Data Display}

    \section*{5. Data Analysis}

    We conducted a $t$-test for the population slope $\beta$ of the least-squares regression line that relates the number of parameters in a model trained on a 100-image subset of the CIFAR-10 dataset to the difference in accuracy between training and test data (Train Accuracy $-$ Test Accuracy).

    \subsection*{5.1 Condition Check}

    \begin{quote}

    \textbf{5.1.1 Linear}

    {The scatterplot of the data shows a clear linear trend, and the residual plot shows no remaining curved pattern. Therefore, the linearity condition is satisfied.}

    \textbf{5.1.2 Independent}

    Each model was trained independently with no interaction between runs. Thus, the independence condition is met by the design of the experiment.

    \textbf{5.1.3 Normal}
    The dotplot of the residuals shows no strong skew and no outliers, suggesting the residuals are approximately normally distributed.

    \textbf{5.1.4 Equal Variance}
    The residual plot shows shows no noticeable $<$ or $>$ shape, so the equal variance condition is satisfied.

    \textbf{5.1.5 Random}
    The parameters of the model were randomized on initialization, so each model can be seen as randomly selected from the population
    of models of the same size and structure.

    \end{quote}

    \subsection*{5.2 Calculations}

    \section*{6. Conclusion}

    \section*{7. Reflection}
